Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Layout and spell check

\begin{figure}[b]
  \begin{center}
    \includegraphics{graphics/research_process.pdf}
    \caption{Outline of the research process}
    \label{fig:researchprocess}
  \end{center}
\end{figure}

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ l l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

@@

		Practices &
		Distinguishable practices that are used or established during transformation.
		Factors that are presented as neutral in terms of successes and challenges
		in the primary studies.
		(coaching, piloting, continuous integration, communities of practice) \\

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family, as the final result
    of coding the primary studies}
    \label{table:codecount}
\end{table}

@@

As an accurate description had been created for each code, the initially defined
categories could be refined. Some codes were recategorized, and the definitions
of a few categories were revisited, until a final ordering was reached. The
results are presented according to the final categorization.

@@

% What public events
Organizations typically strived to increase the agile awareness by introducing
series of events for promoting agile, ranging from public seminars to brown bag
meetings and hands-on workshops. These events were aimed at a general audience,
consisting of all organizational groups. Events were arranged especially in the
beginning of the agile journey. In some cases the demand and interest in public
events was maintained, and the events were continued.
Some cases describe continually arranged agile events serving a central role in
maintaining and advancing further the agile model [P23, P47].
Training events were even productized so that they could be replicated for a
large number of people [P32, P46].

@@

Events and coaching activity were coordinated forms of promoting the new model,
but the agile transformation gave also birth to communities [P3]. Typically
communities were emerging later in the transformation, when the rollout team
was starting to step aside [P3, P41].
In some cases the communities were created by passionate individuals without
corporate intervention, and participation in communities was voluntary [P47].
Communities were created when the mass of people involved became too large for
formal control [P52].
In other cases the forming of communities was stimulated by the organization
[P12, P45].
Companies strived to create communities of practice [P42] or special interest
groups [P41] in order to reinforce continuous learning in the organization.
Communities helped people to form a learning habit, which promoted continuous
improvement in the organization [P52].

@@

Even though the organization was in a state of transformation the workload of
teams was not always adjusted to facilitate the process.
Some organizations started their agile journey in a state where people were
overcommitted. It was later realized that when people are overloaded they will
not be able to changing their behavior and learn new ways of working [P37, P42].
Spayd [P49] also describes how senior management pressed teams to deliver what
the customer had been promised, regardless of what the current velocity of
development predicted. For one part the pressure to deliver interfered with the
transformation, but it was also forcing a change in the old way of working
[P49].

In one case management forced people to remain committed to firm deadlines, even
midst in the organizational transformation [P21]. The engagement in old
commitments and tasks resulted in ignoring new practices introduced by agile,
and eventually the agile method was breaking down [P21].
Cowan [P11] describes how time was allocated for tending to old commitments.
However, even when there was preparation for extra work people with specific
expertise became overloaded. After time it was realized that overcommitment must
be reduced by allowing to shift excess work for later time [P11].

@@

In this chapter we discuss the results and provide a conclusion on this work.
First the results are discussed, including highlighting of most important
findings and comparison to previous work. Then we present limitations and
thereats to the validity of this work. This chapter ends with a concluding
overview of the work.

@@

* Recap of mosti important results

>>>>

\begin{figure}
  \begin{center}
    \includegraphics{graphics/research_process.pdf}
    \caption{Outline of the research process}
    \label{fig:researchprocess}
  \end{center}
\end{figure}

@@

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

		Practices &
		Distinguishable practices that are used or established during transformation.
		Factors presented as neutral relating to successes and challenges.
		(coaching, piloting, continuous integration, communities of practice) \\

@@

\begin{table}
    \centering
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family, as the final result
    of coding the primary studies}
    \label{table:codecount}
\end{table}

@@

As an accurate description had been created for each code, the initially defined
categories could be refined. Some codes were re-categorized, and the definitions
of a few categories were revisited, until a final ordering was reached. The
results are presented according to the final categorization.

@@

% What public events
Organizations were typically striving to increase the agile awareness by introducing
series of events for promoting agile, ranging from public seminars to brown bag
meetings and hands-on workshops. These events were aimed at a general audience,
consisting of all organizational groups. Events were arranged especially in the
beginning of the agile journey. In some cases the demand and interest in public
events was maintained, and the events were continued.
Some cases describe continually arranged agile events serving a central role in
maintaining and advancing further the agile model [P23, P47].
Training events were even productized so that they could be replicated for a
large number of people [P32, P46].

@@

Events and coaching activity were coordinated forms of promoting the new model,
but the agile transformation gave also birth to communities [P3]. Typically
communities were emerging later in the transformation, when the rollout team
was starting to step aside [P3, P41].
In some cases the communities were created by passionate individuals without
corporate intervention, and participation in communities was voluntary [P47].
Communities were created when the mass of people involved became too large for
formal control [P52].
In other cases the forming of communities was stimulated by the organization
[P12, P45].
Companies were striving to create communities of practice [P42] or special interest
groups [P41] in order to reinforce continuous learning in the organization.
Communities helped people to form a learning habit, which promoted continuous
improvement in the organization [P52].

@@

Even though the organization was in a state of transformation the workload of
teams was not always adjusted to facilitate the process.
Some organizations started their agile journey in a state where people were
over-committed. It was later realized that when people are overloaded they will
not be able to changing their behavior and learn new ways of working [P37, P42].
Spayd [P49] also describes how senior management pressed teams to deliver what
the customer had been promised, regardless of what the current velocity of
development predicted. For one part the pressure to deliver interfered with the
transformation, but it was also forcing a change in the old way of working
[P49].

In one case management forced people to remain committed to firm deadlines, even
midst in the organizational transformation [P21]. The engagement in old
commitments and tasks resulted in ignoring new practices introduced by agile,
and eventually the agile method was breaking down [P21].
Cowan [P11] describes how time was allocated for tending to old commitments.
However, even when there was preparation for extra work people with specific
expertise became overloaded. After time it was realized that over-commitment must
be reduced by allowing to shift excess work for later time [P11].

@@

In this chapter we discuss the results and provide a conclusion on this work.
First the results are discussed, including highlighting of most important
findings and comparison to previous work. Then we present limitations and
threats to the validity of this work. This chapter ends with a concluding
overview of the work.

@@

* Recap of most important results
